Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Prediction in the Swiss Alps

### 2016-12-21 Optimization case study - JoH/elsarticle-template.tex
Renaming files.
JoH paper under correction.

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
	\label{fig:crossing_4Zo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig07.pdf}}
	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo-2MIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
	\label{fig:figure_crpss_4Zo-2HIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
	\caption{Number of analogues for the different regions and the various methods resulting from the optimization. Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
	\label{fig:figure_nb_analogs}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
	\label{fig:crossing_4Zo-2MIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods. The results are those of the 10 subregions. The geopotential heights are sorted by increasing pressure and hour.}
	\label{fig:levels_weights_average}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=7.5cm]{figures/fig17.pdf}}
	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}

@@

\begin{table}[t]
	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
			\hline 
			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo}
\end{table}

@@

\begin{table}[t]
	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
			\hline 
			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo-2MIo}
\end{table}

>>>>

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig04.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
	\label{fig:crossing_4Zo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo-2MIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig06.pdf}}
	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
	\label{fig:figure_crpss_4Zo-2HIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
	\caption{Number of analogues for the different regions and the various methods resulting from the optimization. Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
	\label{fig:figure_nb_analogs}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig08.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
	\label{fig:crossing_4Zo-2MIo}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods. The results are those of the 10 subregions. The geopotential heights are sorted by increasing pressure and hour.}
	\label{fig:levels_weights_average}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=7.5cm]{figures/fig10.pdf}}
	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}

@@

\begin{table}[t]
	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
			\hline 
			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo}
\end{table}

@@

\begin{table}[t]
	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline 
			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
			& CP & VP & CP & VP & CP & VP \\ 
			\hline 
			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
			\hline 
			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:scores_thresholds_4Zo-2MIo}
\end{table}
